Why there are more species in several small patches vs few large patches:

### 2024-03-19 ms_SLOSS.Rmd
Changes to submit

Leonardo A. Saravia ^1^^2^, Ulises Balza ^1^, Fernando Momo^3^^4^

1. Centro Austral de Investigaciones Científicas (CADIC-CONICET). Houssay 200 (9410), Ushuaia, Argentina.

2. Universidad Nacional de Tierra del Fuego (UNTDF), Yrigoyen 879 (9410), Ushuaia, Argentina

3. Instituto de Ciencias. Universidad Nacional de General Sarmiento. J.M. Gutierrez 1159 (1613), Los Polvorines, Argentina.

4. Departamento de Ciencias Básicas. Universidad Nacional de Luján. Rutas 5 y 7, (6700) Luján. Argentina.

@@

@@

The model was developed in Netlogo 6.3.0 and the model source code is available at Github <https://github.com/lsaravia/DynamicForestExtinction>, the Overview, Design concepts, Details (ODD), protocol for describing individual-based models is included within the model source code [@Grimm2010]. We performed the simulations and analysis using R version 4.3.1 [@RCoreTeam2023], the R source code to perform simulations and analysis is located at <https://github.com/EcoComplex/multiSLOSS>.

>>>>

@@

Habitat fragmentation, biodiversity, spatially explicit models, multi-species models, neutral theory, competitive theory, habitat selection, dispersal, extinction, reproduction.

@@

The model was developed in Netlogo 6.3.0 and the model source code is available at Github <https://>, the Overview, Design concepts, Details (ODD), protocol for describing individual-based models is included within the model source code [@Grimm2010]. We performed the simulations and analysis using R version 4.3.1 [@RCoreTeam2023], the R source code to perform simulations and analysis is located at <https://>.
